Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library. 
For example, our Zip transformations are 78 lines of code, compared to 1600 lines of code for a
   hand-written parser. Additionally, Nail provides convenient and safe interfaces for allocating
   memory and accessing streams that address the most common occurences of buffer overflow
   vulnerabilities.

>>>>

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library. 
For example, our Zip transformations are 78 lines of code, compared to 1600 lines of code for a
   hand-written parser. Additionally, Nail provides convenient and safe interfaces for allocating
   memory and accessing streams that address the most common occurrences of buffer overflow
   vulnerabilities.
